Terrain is a stronger predictor of peat depth than airborne radiometrics in Norwegian landscapes

### 2025-08-29 ms/ms.Rmd
add data archive to reference list
as requested by Copernicus production office

All point measurements described above were ultimately aggregated to 10 m resolution by taking the mean of point values within each cell, inversely weighted by their distances to the cell center.

>>>>

All point measurements described above [@volleringPeatDepthOccurrence2025] were ultimately aggregated to 10 m resolution by taking the mean of point values within each cell, inversely weighted by their distances to the cell center.

### 2025-08-29 ms/ms.tex
add data archive to reference list
as requested by Copernicus production office

All point measurements described above were ultimately aggregated to 10 m resolution by taking the mean of point values within each cell, inversely weighted by their distances to the cell center.

>>>>

All point measurements described above \citep{volleringPeatDepthOccurrence2025} were ultimately aggregated to 10 m resolution by taking the mean of point values within each cell, inversely weighted by their distances to the cell center.
